
\begin{itemize}
\item{\textit{What is you user ID constructed from?}

    email
  }
\item{\textit{What are the permissions for ``.gnupg'' and what do they mean?}

    Should be 700, only owner should be able to read/use/traverse the gpg related
    files/folders (sockets, keyring, etc)
  }
\item{\textit{Is it a good idea to store the revocation certificate on the same
      device as your key-pair?}

    As long as it is not the only place it is stored it should be fine, if it is
    the only place it is stored then no. You should always be able to revoke
    your key incase it gets compromised/lost. A revocation certificate makes the
    key-pair invalid from there on, though that is not to say that people will
    not use it for communication (e.g. a user not refreshing keys in their
    keyring). 
  }
\item{\textit{What were those messages transmitted and received from the
other lab group? \(If they are long, show them onscreen to the assistant\)}
#
# /etc/hosts: static lookup table for host names
#

#<ip-address>	<hostname.domain.org>	<hostname>
127.0.0.1		localhost
::1			localhost

130.236.254.194		muspaj.lysator.liu.se	muspaj
2001:6b0:17:f0a0::c2	muspaj.lysator.liu.se	muspaj

130.236.254.1		liunet-gw.lysator.liu.se	liunet-gw
130.236.254.2		ns-master.lysator.liu.se	ns-master
130.236.254.4		ns-slave.lysator.liu.se		ns-slave
130.236.254.5		ns.lysator.liu.se		ns
2001:6b0:17:f0a0::5	ns.lysator.liu.se		ns
130.236.254.7		nis.lysator.liu.se		nis
2001:6b0:17:f0a0::7	nis.lysator.liu.se		nis
130.236.254.25		hoover.lysator.liu.se		hoover loghost
130.236.254.125		as-master.lysator.liu.se	as-master
130.236.254.126		as-slave.lysator.liu.se		as-slave
130.235.254.225		resolver.lysator.liu.se		resolver
2001:6b0:17:f0a0::e1	resolver.lysator.liu.se		resolver

130.236.254.222 vindbrygga.lysator.liu.se vindbrygga
2001:6b0:17:f0a0::de vindbrygga.lysator.liu.se vindbrygga

# End of file


    
  }
\item{\textit{At what time was this document signed?}
        Signature made Fri 09 Sep 2016 20:50:30 CEST using RSA key ID 239AD40D
    
  }
\item{\textit{Can you be sure that the key belongs to the assistant?}
    No, because I have not verified the validity of the key. Meaning I do not
    know 
  }
\item{\textit{Have you returned the signed keys in your keyring?}

    Yes, check my other keys (knase@lysator.liu.se)
    
}


\end{itemize}